Community Embeddings with Bayesian Gaussian Mixture Model and Variational Inference\\ \thanks{The reported study was partially supported by RFBR grant \textnumero 20-07-00958. The paper was prepared within the framework of the HSE University Project Group Competition 2020-2022.}

### 2022-05-21 paper-ComE-BGMM-VI.tex
Implement Feedback from 18.05.2022

The recent \citeyear{ComE} graph embeddings algorithm ComE is extended similarily to the \citeyear{ComE+} ComE+ by taking a Bayesian approach. The open-source code for the Bayesian approach to ComE's community embedding is published on GitHub\footnote{at \url{https://github.com/abegehr/ComE_BGMM}} and serves as a contribution to community embedding research \cite{ComE_BGMM_GH}.

@@

Multiple surveys and articles on graph embeddings were consulted to build a full picture of the current state of graph embedding research. Especially the \citeyear{Goyal_2018} survey \textit{Graph Embedding Techniques, Applications, and Performance: A Survey} by \citeauthor{Goyal_2018} and the \citeyear{rossi20tkdd-roles} paper \textit{On Proximity and Structural Role-based Embeddings in Networks: Misconceptions, Techniques, and Applications} by \citeauthor{rossi20tkdd-roles} have proven to be primary resources for understanding the current landscape of graph embedding research \cite{Goyal_2018, rossi20tkdd-roles}.

@@

@@

\begin{table}[htbp]
    \centering
    \caption{Hyperparameters used by \citeauthor{ComE_GH}'s implementation of ComE \cite{ComE_GH}.}
    \label{table:params_ComE}
    \begin{tabularx}{\linewidth}{ l | c | X }
        parameter            & notation & description                                                                     \\
        \hline
        \hline
        number\_walks        & $\gamma$ & number of random walks for each node                                            \\
        \hline
        walk\_length         & $\ell$   & length of each walk                                                             \\
        \hline
        representation\_size & $D$      & dimensionality of the embedding                                                 \\
        \hline
        num\_workers         & \empty   & number of threads                                                               \\
        \hline
        num\_iter            & \empty   & number of overall iterations                                                    \\
        \hline
        com\_n\_init         & \empty   & number of initializations to run on the communtiy embedding model (GMM or BGMM) \\
        \hline
        reg\_covar           & \empty   & regularization coefficient for ensuring positive covariance                     \\
        \hline
        batch\_size          & \empty   & size of the batch                                                               \\
        \hline
        window\_size         & $\zeta$  & windows size used to compute the context embedding                              \\
        \hline
        negative             & $m$      & number of negative samples                                                      \\
        \hline
        lr                   & \empty   & learning rate                                                                   \\
        \hline
        alpha                & $\alpha$ & Trade-off parameter for context embedding                                       \\
        \hline
        beta                 & $\beta$  & Trade-off parameter for community embedding                                     \\
        \hline
        down\_sampling       & \empty   & perform down sampling of common nodes                                           \\
        \hline
        communities          & $K$      & number of communities                                                           \\
    \end{tabularx}
\end{table}

@@

\begin{table}[htbp]
    \centering
    \caption{Hyperparameter added to ComE for supporting a BGMM for community embedding \cite{ComE_BGMM_GH}.}
    \label{table:params_ComE_BGMM}
    \begin{tabularx}{\linewidth}{ l | c | X }
        parameter                    & notation & description                               \\
        \hline
        \hline
        weight\_concentration\_prior & $\Gamma$ & Bayesian GMM's weight concentration prior \\
    \end{tabularx}
\end{table}

>>>>

The recent \citeyear{ComE} graph embeddings algorithm ComE is extended similarily to the \citeyear{ComE+} ComE+ by taking a Bayesian approach. The open-source code for the Bayesian approach to ComE's community embedding is published on GitHub\footnote{at \url{https://github.com/abegehr/ComE_BGMM}} and serves as a contribution to community embedding research \cite{ComE_BGMM_GH}. The source code is written in Python and tested with Python 3.6.10. For node and context embedding, ComE's training\_sdg\_inner Cython binary is utilized \cite{van1995python, ComE_GH}.

@@

Surveys and articles on graph embeddings were consulted to build a full picture of the current state of graph embedding research. Especially the \citeyear{Goyal_2018} survey \textit{Graph Embedding Techniques, Applications, and Performance: A Survey} by \citeauthor{Goyal_2018} and the \citeyear{rossi20tkdd-roles} paper \textit{On Proximity and Structural Role-based Embeddings in Networks: Misconceptions, Techniques, and Applications} by \citeauthor{rossi20tkdd-roles} have proven to be primary resources for understanding the current landscape of graph embedding research \cite{Goyal_2018, rossi20tkdd-roles}.

@@

During implementation, data transformation, testing, and plotting the following libraries and frameworks have proved invaluable: NumPy, Pandas, Matplotlib, NetworkX, and Jupyter Notebooks \cite{harris2020array, mckinney-proc-scipy-2010, reback2020pandas, Hunter:2007, SciPyProceedings_11, Kluyver2016jupyter}.

@@

\begin{table}[H]
    \centering
    \caption{Hyperparameters used by \citeauthor{ComE_GH}'s implementation of ComE \cite{ComE_GH}.}
    \label{table:params_ComE}
    \begin{tabularx}{\linewidth}{ l | c | X }
        parameter            & notation & description                                                                     \\
        \hline
        \hline
        number\_walks        & $\gamma$ & number of random walks for each node                                            \\
        \hline
        walk\_length         & $\ell$   & length of each walk                                                             \\
        \hline
        representation\_size & $D$      & dimensionality of the embedding                                                 \\
        \hline
        num\_workers         & \empty   & number of threads                                                               \\
        \hline
        num\_iter            & \empty   & number of overall iterations                                                    \\
        \hline
        com\_n\_init         & \empty   & number of initializations to run on the communtiy embedding model (GMM or BGMM) \\
        \hline
        reg\_covar           & \empty   & regularization coefficient for ensuring positive covariance                     \\
        \hline
        batch\_size          & \empty   & size of the batch                                                               \\
        \hline
        window\_size         & $\zeta$  & windows size used to compute the context embedding                              \\
        \hline
        negative             & $m$      & number of negative samples                                                      \\
        \hline
        lr                   & \empty   & learning rate                                                                   \\
        \hline
        alpha                & $\alpha$ & trade-off parameter for context embedding                                       \\
        \hline
        beta                 & $\beta$  & trade-off parameter for community embedding                                     \\
        \hline
        down\_sampling       & \empty   & perform down sampling of common nodes                                           \\
        \hline
        communities          & $K$      & number of communities                                                           \\
    \end{tabularx}
\end{table}

The hyperparameters number\_walks, walk\_length, and representation\_size are utilised in the node embedding step Node2Vec to achieve an initial node embedding optimizing for first and second oder proximity. reg\_covar,  batch\_size, window\_size, negative, and lr are utilized in the context embedding step. num\_workers is a performance parameter which allows multithreading the node embedding or context embedding steps. num\_iter, and com\_n\_init control the number of iterations to run over ComE's closed loop algorithm and how many random initialisations of the community embedding to try out, respectivelly. alpha and beta allow adjusting the weighting between context and community embedding. Communities $K$ is the number of Gaussian generators as pertained to the Gaussian Mixture Model.

@@

\begin{table}[H]
    \centering
    \caption{Hyperparameter added to ComE for supporting a BGMM for community embedding \cite{ComE_BGMM_GH}.}
    \label{table:params_ComE_BGMM}
    \begin{tabularx}{\linewidth}{ l | c | X }
        parameter                    & notation & description                               \\
        \hline
        \hline
        weight\_concentration\_prior & $\Gamma$ & Bayesian GMM's weight concentration prior \\
    \end{tabularx}
\end{table}
